% !TEX root = Document.tex
% !TeX spellcheck = en
% Abstract
%
%   Résumé de la recherche écrit en anglais sans être
% une traduction mot à mot du résumé écrit en français.

\chapter*{ABSTRACT}\thispagestyle{headings}
\addcontentsline{toc}{compteur}{ABSTRACT}
%
\begin{otherlanguage}{english}

Robotics is a branch of engineering dealing with the creation of machines capable
of helping or even replacing humans in tasks which can be dull, dirty or dangerous.
Most commonly used in the fields of manufacturing and search and rescue, in recent
years robotics has found its place in surveying and infrastructure inspection
thanks to their increased mobility and their ability to tackle repetitive tasks.
However, today's robots are still often remote controlled with only
partial autonomy and still aren't capable of decision making and navigation.

In this thesis, we address this problem by presenting two methods allowing a robot
to navigate around a structure to inspect its surface. First, we tackle
the problem of ground based inspections of the visible part of a bounded closed
structure. Using an unmanned ground vehicle equipped with a depth sensor, our
method allows us to map the entire surface of the structure. Our specific
contribution here, is a system capable of performing the inspection while also
minimizing errors on the robot's localization system. Also known as "active slam",
we perform path planning for exploration while also performing SLAM. Second, we
propose a system specifically tailored to the inspection of wind turbines. Using
an unmanned aerial vehicle equipped with 2D laser scanners, our method allows
a quadcopter to take off, climb up the tower and inspect the front facing
surface of the turbine's blades.

Both of our systems are implemented and shown to work within simulation environments.
Our ground based inspection is also demonstrated in real indoor experiments where
we show how to deal with noise not accounted for in simulation.
Finally, we also show preliminary results on the deployment of our wind turbine inspection
system.

\end{otherlanguage}
